\documentclass[a4paper,10pt]{article}

% Hier die Nummer des Blatts und Autoren angeben.
\newcommand{\blatt}{1}
\newcommand{\autor}{ UX-DDDDesign / Maurice Da Cruz Guerreiro, Lara-Marie Ehlen, Henry Sheng-Long Hon, Julian Mühlbauer, Nils Berg }

\usepackage{hci}
% Extra packages for better table handling
\usepackage{tabularx}
\usepackage{caption}
\captionsetup[table]{position=bottom,font=small}
\usepackage{setspace}
\setstretch{0.97}
% Reduce vertical spacing between paragraphs
\setlength{\parskip}{0pt}
% Tighten spacing around floats and captions
\setlength{\intextsep}{8pt plus 2pt minus 2pt}
\setlength{\textfloatsep}{10pt plus 2pt minus 2pt}
\setlength{\floatsep}{8pt plus 2pt minus 2pt}
\captionsetup{skip=4pt}
% Reduce spacing around sectioning commands (especially \paragraph)
\usepackage{titlesec}
\titlespacing*{\section}{0pt}{8pt plus 2pt minus 2pt}{4pt plus 1pt minus 1pt}
\titlespacing*{\subsection}{0pt}{6pt plus 2pt minus 2pt}{3pt plus 1pt minus 1pt}
\titlespacing*{\paragraph}{0pt}{2pt plus 1pt minus 1pt}{0.5em}

\begin{document}
% Seitenkopf mit Informationen
    \kopf
    \renewcommand{\figurename}{Figure}

    \title{PACT Analyzation Amazon Echo 8}


    \section{People}\label{sec:people}
    Supports a wide range of users from different backgrounds and ages via voice and touch interaction.

    \begin{table}[htbp]
        \centering
        % Make table fit the text width and wrap long text
        \begin{tabularx}{\textwidth}{|l|X|l|X|}
            \hline
            \textbf{User Group}      & \textbf{Usage}                                           & \textbf{Age} & \textbf{Device Usage}                         \\
            \hline
            Families                 & Entertainment, Smart Home control and communication      & 8 to 60      & One device per household                      \\
            \hline
            Smart Home enthusiasts   & Smart Home control, automation                           & 18 to 40     & One user uses many devices from one ecosystem \\
            \hline
            Elderly people           & Support in daily tasks and communication                 & 60+          & One to two persons share one device           \\
            \hline
            People with disabilities & Support in otherwise challenging tasks and communication & 5+           & One person uses one device \\
            \hline
        \end{tabularx}
        \caption{User groups, usage, age, and device usage for Amazon Echo 8}
        \label{tab:user-groups}
    \end{table}


    \section{Activities}\label{sec:activities}

    \paragraph{Media and entertainment}
    Playback of audio and video streaming on the 8-inch display.
    Voice-first control is supported by touch when needed.

    \paragraph{Smart home control}
    Operation of lights, thermostats, plugs, and routines/automation.
    Interactions are typically short commands with occasional multistep dialogs for setup.

    \paragraph{Communication}
    Voice and video calls, announcements, messaging across household members and contacts.

    \paragraph{Information and assistance}
    Timers, alarms, reminders, weather, shopping lists, translations, and quick research.

    \paragraph{Accessibility}
    Hands-free operation, natural language commands, guided multistep interactions that reduce cognitive and motor load.

    \section{Contexts}\label{sec:contexts}

    \paragraph{Physical}
    Living room, kitchen, and bedroom use with varying noise and lighting.
    The device is typically used at a 1--5 m distance in shared spaces.

    \paragraph{Social}
    Individual and family use, including guests and children, with differing privacy expectations in shared households.

    \paragraph{Organizational and technical}
    Amazon account(s), household profiles, Wi\-Fi dependency, and skills/devices within the same ecosystem with clear data protection expectations.

    \section{Technologies}\label{sec:technologies}

    \paragraph{Inputs}
    Microphone for voice input, touch input on the 8-inch display, camera for video calls, Bluetooth for pairing.
    Control via Smartphone App.

    \paragraph{Outputs}
    Builtin speaker and the 8-inch screen for feedback and media, status LEDs.

    \paragraph{Connectivity and integration}
    Wi\-Fi and Bluetooth connectivity, an extensible Alexa ecosystem, support for smart home hubs/standards like matter via compatible devices.
    Account linking via Cloud Services and smartphone apps.

    \paragraph{Constraints and risks}
    Requires power and network connectivity and account linking.
    Privacy controls include mic mute and a camera shutter.
    When voice fails, users can fall back to touch or the smartphone app.
    Purchases use confirmations.
    Parental control is supported via the smartphone app.


    \section{Conclusion}\label{sec:conclusion}
    The Echo Show 8 serves diverse users in shared home environments through voice-first, screen-supported interaction.
    Typical activities are brief, repeatable, and benefit from automation and multimodal feedback.
    Success depends on robust speech recognition, clear confirmations, privacy controls, and seamless integration with household accounts and smart devices.

\end{document}
